### 2015-04-13 src/intro/intro.tex
Fixed panel labels

The semicircular canals measure the three-dimensional rotational velocity of the head. Each side of the head contains three orthogonally oriented canals allowing for rotation to be perceived in all three dimensions. Each of the six canals consists of a circular tube filled with a fluid known as endolymph (see \figref{intro:fig:canals}A). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, that separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see \figref{intro:fig:canals}B). While the inertial fluid motion suggests that the cupula should be sensitive to angular acceleration, reactive forces resulting from the fluid motion, such as endolymph viscosity and cupular elasticity,  cause the cupular deflection to reflect angular velocity instead \cite{goldberg2012}.

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/canals.pdf}
    \caption{Detailed view of a semicircular canal \panelref{A} in rest and \panelref{B} during rotation. Inertia of the endolymph in the canal causes the cupula to deflect during rotation.}
    \label{intro:fig:canals}
\end{figure}

@@

\subsubsection{Otoliths}
The linear acceleration and gravitational forces are measured by the two otolith organs on either side of the head: the saccule and the utricule. Each otolith consists of an endolymph filled compartment containing calcium carbonate crystals known as otoconia (\figref{intro:fig:otoliths}A). Due to their high inertia, these otoconia fall behind during linear acceleration (\figref{intro:fig:otoliths}B), and move ahead during deceleration. In addition, they fall downward as a result of the gravitational field (\figref{intro:fig:otoliths}C). The otoconia are mounted on top of a flexible polysaccharide gel, in which hair cells, similar to those found in the semicircular canals, are partly embedded \cite{goldberg2012}.

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/otoliths.pdf}
    \caption{Detailed view of an otolith \panelref{A} in rest, \panelref{B} during head tilt, and \panelref{C} during linear acceleration. The high inertia of the otoconia keeps them from moving rapidly during both head tilt as well as linear acceleration. As the effect is physically identical in either case, head tilt and linear acceleration cannot be disambiguated based on the otolith signal alone.}
    \label{intro:fig:otoliths}
\end{figure}

@@

    \caption{Vection pattern during \panelref{A} lateral translation and \panelref{B} rotation. During translation nearby targets (red) have a larger retinal displacement compared to far away ones (blue). Retinal displacement across rotation does not depend on target distance. }
    \label{intro:fig:vection}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{src/intro/figures/treeframe.pdf}
	\caption{\panelref{A} Trees are aligned with gravity, making them ideal cues for orientation. \panelref{B} The rod-and-frame illusion; even though the frame is rotated, participants might perceive the line as being slanted.}
	\label{intro:fig:treeframe}
\end{figure}

>>>>

The semicircular canals measure the three-dimensional rotational velocity of the head. Each side of the head contains three orthogonally oriented canals allowing for rotation to be perceived in all three dimensions. Each of the six canals consists of a circular tube filled with a fluid known as endolymph (see \panelref{intro:fig:canals}{A}). One part of the tube, the ampulla, is a bit thicker than the rest and contains a membrane, the cupula, that separates the fluid. When the head rotates, the fluid stays behind because of its inertia which in turn causes the membrane to deflect (see \panelref{intro:fig:canals}{B}). While the inertial fluid motion suggests that the cupula should be sensitive to angular acceleration, reactive forces resulting from the fluid motion, such as endolymph viscosity and cupular elasticity,  cause the cupular deflection to reflect angular velocity instead \cite{goldberg2012}.

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/canals.pdf}
    \caption{Detailed view of a semicircular canal \panel{A} in rest and \panel{B} during rotation. Inertia of the endolymph in the canal causes the cupula to deflect during rotation.}
    \label{intro:fig:canals}
\end{figure}

@@

\subsubsection{Otoliths}
The linear acceleration and gravitational forces are measured by the two otolith organs on either side of the head: the saccule and the utricule. Each otolith consists of an endolymph filled compartment containing calcium carbonate crystals known as otoconia (\panelref{intro:fig:otoliths}{A}). Due to their high inertia, these otoconia fall behind during linear acceleration (\panelref{intro:fig:otoliths}{B}), and move ahead during deceleration. In addition, they fall downward as a result of the gravitational field (\panelref{intro:fig:otoliths}{C}). The otoconia are mounted on top of a flexible polysaccharide gel, in which hair cells, similar to those found in the semicircular canals, are partly embedded \cite{goldberg2012}.

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/otoliths.pdf}
    \caption{Detailed view of an otolith \panel{A} in rest, \panel{B} during head tilt, and \panel{C} during linear acceleration. The high inertia of the otoconia keeps them from moving rapidly during both head tilt as well as linear acceleration. As the effect is physically identical in either case, head tilt and linear acceleration cannot be disambiguated based on the otolith signal alone.}
    \label{intro:fig:otoliths}
\end{figure}

@@

    \caption{Vection pattern during \panel{A} lateral translation and \panel{B} rotation. During translation nearby targets (red) have a larger retinal displacement compared to far away ones (blue). Retinal displacement across rotation does not depend on target distance. }
    \label{intro:fig:vection}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{src/intro/figures/treeframe.pdf}
	\caption{\panel{A} Trees are aligned with gravity, making them ideal cues for orientation. \panel{B} The rod-and-frame illusion; even though the frame is rotated, participants might perceive the line as being slanted.}
	\label{intro:fig:treeframe}
\end{figure}
